Manuscript Figures

### 2024-10-04 manuscript_figures.Rmd
fixed metadata

```{r,fig.height = 6, fig.width = 16}
s6d = make_roc_metabolomics(data)

>>>>

m2 = function(data,ncol=5){

    loop = filter(data, row_id == i)

    mod = glm(as.factor(condition) ~ norm_value, 
              data = loop,
              family = "binomial")

     cn = loop %>% 
      pull(compound_name_cleaned) %>% 
      unique()
    #define object to plot
    rocobj <- pROC::roc(loop$condition, predicted)

    auc = round(as.numeric(gsub(".*: ", "",rocobj$auc)),2)

    #Dealing with long names 
    wrapper <- function(x, ...) 
    {
      paste(strwrap(x, ...), collapse = "\n")
    }

    #create ROC plot
    p1 = pROC::ggroc(rocobj)+
      ggtitle(paste0(cn," AUC: ",auc))

    list[[i]] = p1
  }
  plot = do.call("grid.arrange",c(list, ncol = ncol))

  return(plot) 
}

s6d = m2(data)
